Causal Impact of Masks, Policies, Behavior on Early Covid-19 Pandemic in the U.S.

### 2020-09-07 tex/covidEffectOfNPI-revision.tex
minor update

We present a conceptual framework that spells out the causal structure on how the Covid-19 spread is dynamically determined by policies and human behavior. Our approach explicitly recognizes that policies not only directly affect the spread of Covid-19 (e.g., mask requirement) but also indirectly affect its spread by changing people's behavior (e.g., stay-at-home order). It also recognizes that people react to new information on Covid-19 cases and deaths and voluntarily adjust their behavior (e.g., voluntary social distancing and hand washing) even without any policy in place. Our casual model provides a framework to quantitatively decompose the growth of Covid-19 cases and deaths into three components: (1) direct policy effect, (2) policy effect through behavior, and (3) direct behavior effect in response to new information.\footnote{The causal model is framed using the language of structural equations models and causal diagrams of econometrics (\cite{pwright, haavelmo:1944, tinbergen:1940, wold:1954, pearl:biometrika, heckman:pinto}) and genetics \citep{wright1923}, with natural unfolding potential/structiral outcomes representation \citep{rubin1974,tinbergen1930,neyman:PO,imbens_rubin_2015}. The work on causal graphs has been modernized and put on rigorous footing by  \cite{pearl:biometrika}, \cite{pearl:robins}, \cite{pearl:causality}, \cite{pearl:why}, \cite{white:chalak}, \cite{peters2020book}, and \cite{hernanrobins2020book}, with major applications taking place in computer science, econometrics, and epidemiology. The particular causal diagram has several ``mediation" components, where variables affect outcomes directly and indirectly through other variables called mediators; these structures go back at least to \citet[][see Figure 6]{wright1923}; see, e.g., \cite{baron1986}, \cite{Hines2020}, \cite{richardson:mediation} for modern treatments. The father and son, P. Wright and S. Wright closely collaborated to develop structural equation models and causal path diagrams; P. Wright's key work represented supply-demand system as a directed acyclical graph and established its identification using exclusion restrictions on instrumental variables.}

@@

Our estimates imply that nationally implementing mandatory face masks
for employees in public businesses on March 14th would have reduced the
growth rate of cases and that of deaths by approximately 10 percentage
points in late April. As shown in Figure \ref{fig:US-mask-dgrowth},
this leads to reductions of $21$\% and $34$\% in cumulative reported
cases and deaths, respectively, by the end of May with 90 percent
confidence intervals of $[9,32]$\% and $[19,47]$\%, which roughly
implies that 34 thousand lives could have been saved.
%\footnote{These estimates
%are slightly lower than those reported in earlier releases of the paper on ArXiv.
%One of the reason is that we chose to focus on a simplified version of the model 
%as our base model, by averaging business closure policies as measure of shutdown. This produced more stable results when
%conducting sensitivity results, in particular using fixed effects estimators.  
%We also present several variants of base model, including
%one with separate shutdown policies, in which the effects are slightly larger, in line
%with the previous findings, but we focus reporting counterfactuals only 
%for the base model. } 
This finding is
significant: given this potentially large benefit of reducing the
spread of Covid-19, mandating masks is an attractive policy instrument
especially because it involves relatively little economic
disruption. These estimates contribute to the ongoing efforts towards
designing approaches to minimize risks from reopening
\citep{stock2020b}.

@@

@@

The exogeneity restrictions on the stochastic shocks are as follows:
\begin{equation}\label{eqn:SEM2} \tag{E}
\begin{aligned}
   & \varepsilon^y_{it} &  \perp &  \quad (\varepsilon^b_{it}, \varepsilon^p_{it}, {\wcolor W_{it}}, {\icolor I_{it}}), \\
&  \varepsilon^b_{it}  & \perp & \quad  (\varepsilon^p_{it}, {\wcolor W_{it}}, {\icolor I_{it}}), \\
&   \varepsilon^p_{it} &  \perp &  \quad ({\wcolor W_{it}}, {\icolor I_{it}}),
\end{aligned}
\end{equation}
where we say that $V \perp U$ if $\Ep VU = 0$.\footnote{ An alternative useful
starting point is to impose the Rubin-Rosenbaum type unconfoudedness condition:
$$
Y_{i,t+\ell} (\cdot,\cdot,\cdot)  \indep (P_{it}, B_{it}, I_{it})  \mid W_{it}, \
B_{it} (\cdot,\cdot)  \indep (P_{it}, I_{it})  \mid W_{it}, \
 P_{it} (\cdot)  \indep  I_{it}  \mid W_{it},
$$
which imply, with treating stochastic errors as independent additive components, the orthogonal conditions stated above.} This is a standard way of representing restrictions on errors in structural equation modeling.\footnote{The structural equations of this form are connected to triangular structural equation models, appearing in microeconometrics and macroeconometrics (SVARs), going back to the work of  \cite{strotz1960recursive}.}

@@

The specification of the model above grasps one-period responses.  The dynamics over multiple periods will be induced by the evolution
of information variables, which include time, lagged and integrated values of outcome:\footnote{Our empirical analysis also considers a specification in which information variables include lagged national cases/deaths as well as lagged behavior variables.}
\begin{equation}\label{eq:I}\tag{I}
 {\icolor I_{it} } := I(t, {\ycolor Y_{it}},  { \icolor  I_{i, t-1} })' := \Big (g(t) , {\ycolor Y_{it}},  \sum_{m=0}^{t/\ell}
{\ycolor Y_{i,t - \ell m}} \Big )  \end{equation}
 for  each  $t \in \{0,1,...,T\}$, where $g$ is deterministic function of time, e.g., month indicators,
 and $t/\ell$ is defined as $\lfloor {t/\ell} \rfloor$.

@@

\begin{quote}
\textsc{Structural Equations Model (SEM)}.  Let $i \in \{1,..., N\}$ denote the observational unit,  $t$ be the time periods, and $\ell$ be the time delay.  (1) For each $i$ and $t \leq -\ell$, the confounder, information, behavior, and policy variables $W_{it}, I_{it},  B_{it}, P_{it}$ are determined outside of the model, and the outcome variable $Y_{i, t+\ell}$ is determined outside of the model for $t \leq 0$.  (2) For each $i$ and $t \geq -\ell$, confounders $W_{it}$ are  determined, and information variables $I_{it}$ are determined  by (I); policy variables $P_{it}$ are determined by setting $\iota = I_{it}$  in (P) with  a realized stochastic shock $\varepsilon^p_{it}$ that obeys the exogeneity condition (E);  behavior variables $B_{it}$ are determined by setting $\iota = I_{it}$ and $p= P_{it}$ in  (SO) with a shock $\varepsilon^b_{it}$ that obeys (E); finally, the outcome $Y_{i, t + \ell}$ is realized by setting $\iota = I_{it}$, $p= P_{it}$, and $b = B_{it}$ in  (SO) with a shock $\varepsilon^y_{it}$ that obeys (E). \end{quote}

@@

We  also consider simple counterfactual exercises, where we examine the effects of setting
a sequence of counterfactual policies for each state:
\begin{equation} \label{p-cf}\tag{CF-P}
\{{\pcolor P^\star_{it}} \}_{t=1}^T, \quad i=1, \ldots N.
\end{equation}
We assume that the SEM remains invariant, except for the policy equation.\footnote{It is possible to consider counterfactual exercises in which policy  responds to information through the policy equation if we are interested in endogenous policy responses to information. Counterfactual experiments with endogenous government policy would be important, for example, to understand the issues related to the lagged response of government policies to higher infection rates due to incomplete information. } Given the policies, we generate the counterfactual
outcomes, behavior, and information by propagating the dynamic equations:
\begin{equation} \label{eqn:CF-SEM} \tag{CF-SEM}
  \begin{aligned}
& {\ycolor Y^\star_{i,t+\ell}}  & := & Y_{i,t+\ell} ( {\bcolor B^\star_{it} } , {\pcolor P^\star_{it}}, {\icolor I^\star_{it}}), \\
& {\bcolor B^\star_{it} } & := &   B_{it}({\pcolor P^\star_{it} } ,{\icolor I^\star_{it}}), \\
& {\icolor I^\star_{it} }& := &  I ({ t,  {\ycolor Y^\star_{it}}, \icolor I^\star_{i,t-\ell}}),  \end{aligned}
\end{equation}
with the same initialization as the factual system up to $t \leq 0$. In stating this counterfactual system of equations, we assume that structural outcome equations (SO) and information equations (I) remain invariant and so do the stochastic shocks, decomposed
into observable and unobservable parts. Formally, we record this assumption and above discussion as follows.

\begin{quote}
\textsc{Counterfactual Structural Equations Model (CF-SEM)}.  Let $i \in \{1,..., N\}$ be the observational unit, $t$ be time periods, and $\ell$ be the time delay. (1) For each $i$ and $t \leq 0$, the confounder, information, behavior, policy, and outcome variables are determined as in SEM: $W^\star_{it}= W_{it}$, $I^\star_{it}= I_{it}$,  $B^\star_{it} = B_{it}$, $P^\star_{it}=P_{it}$, $Y^\star_{it} =Y_{it}$.  (2) For each $i$ and $t \geq 0$, confounders $W^\star_{it} =W_{it}$ are determined, and information variables $I^\star_{it}$ are determined  by (I);  policy variables $P^\star_{it}$ are set in (\ref{p-cf}); behavior variables $B^\star_{it}$ are determined by setting $\iota = I^\star_{it}$ and $p= P^\star_{it}$ in  (SO) with  the same stochastic shock $\varepsilon^b_{it}$ in (SO); the  counterfactual outcome $Y^\star_{i, t + \ell}$ is realized by setting $\iota = I^\star_{it}$, $p= P^\star_{it}$, and $b = B^\star_{it}$ in  (SO) with the same stochastic shock $\varepsilon^y_{it}$ in  (SO).
\end{quote}

@@

The dynamic effects take the form:
$$
\begin{array}{lll}
  & \mathrm{DynE}^\star_{it} &=
  \sum_{m=1}^{t/\ell} \left( (\gamma \alpha)_2 + \mu_2+  (\gamma \alpha)_3+ \mu_3    \right)^m \left(\mathrm{PEB}^\star_{i,t-m \ell } +  \mathrm{PED}^\star_{i,t- m\ell} \right)
  \\
 &&  + \sum_{m=1}^{t/\ell-1} \left( (\gamma \alpha)_3 + \mu_3    \right)^m \left (\mathrm{PEB}^\star_{i,t-(m +1) \ell } +  \mathrm{PED}^\star_{i,t- (m+1)\ell}  \right),
 \end{array}
 $$
 interpreting $t/\ell$ as $\lfloor t/\ell \rfloor$.
 The effects can be decomposed into (a) delayed policy effects via behavior by
summing terms containing $PEB$ and (b) delayed policy effects via direct impact
by summing terms containing $PED$.

All counterfactual quantities and contrasts can be computed from the expressions given
above. For examples, given $\Delta C_{i0}>0$, new cases are linked to growth rates via relation:
$$
\frac{\Delta C^{\star}_{it}}{\Delta C_{i0}} = \exp\left (  \sum_{s=1}^t  Y^\star_{is} \right) \text{ and }\frac{ \Delta C_{it}}{\Delta C_{i0}} = \exp
\left (  \sum_{s=1}^t Y_{is}\right).
$$
The cumulative cases can be constructed by summing over the new cases. Various contrasts are
then calculated from these quantities. For example, the relative contrast of new counterfactual cases
to the  factual cases is given by:
$$
\Delta C^{\star}_{it}/\Delta C_{it} = \exp\left(  \sum_{s=1}^t ( Y^\star_{is} -  Y_{is}) \right).
$$
We refer to the appendix for further details. Similar calculations apply for fatalities. 
Note that our analysis is conditional on the factual history and structural stochastic 
shocks.\footnote{For unconditional counterfactual,
we need to make assumptions about the evolution of stochastic shocks appearing in $Y_{it}$. See, e.g, previous
versions of our paper in ArXiv, where unconditional counterfactuals were calculated by assuming stochastic shocks
are i.i.d. and resampling them from the empirical distribution. The differences between conditional and unconditional
contrasts were small in our empirical analysis.}

>>>>

We present a conceptual framework that spells out the causal structure on how the Covid-19 spread is dynamically determined by policies and human behavior. Our approach explicitly recognizes that policies not only directly affect the spread of Covid-19 (e.g., mask requirement) but also indirectly affect its spread by changing people's behavior (e.g., stay-at-home order). It also recognizes that people react to new information on Covid-19 cases and deaths and voluntarily adjust their behavior (e.g., voluntary social distancing and hand washing) even without any policy in place. Our casual model provides a framework to quantitatively decompose the growth of Covid-19 cases and deaths into three components: (1) direct policy effect, (2) policy effect through behavior, and (3) direct behavior effect in response to new information.

@@

Our estimates imply that nationally implementing mandatory face masks
for employees in public businesses on March 14th would have reduced the
growth rate of cases and that of deaths by approximately 10 percentage
points in late April. As shown in Figure \ref{fig:US-mask-dgrowth},
this leads to reductions of $21$\% and $34$\% in cumulative reported
cases and deaths, respectively, by the end of May with 90 percent
confidence intervals of $[9,32]$\% and $[19,47]$\%, which roughly
implies that 34 thousand lives could have been saved. %\footnote{These estimates
%are slightly lower than those reported in earlier releases of the paper on ArXiv,
%One of the reason is that we chose to focus on a simplified version of the model 
%as our base model, by averaging business closure policies as measure of shutdown. This produced more stable results when
%conducting sensitivity results, in particular using fixed effects estimators.  
%We also present several variants of base model, including
%one with separate shutdown policies, in which the effects are slightly larger, in line
%with the previous findings, but we focus reporting counterfactuals only 
%for the base model. } 
This finding is
significant: given this potentially large benefit of reducing the
spread of Covid-19, mandating masks is an attractive policy instrument
especially because it involves relatively little economic
disruption. These estimates contribute to the ongoing efforts towards
designing approaches to minimize risks from reopening
\citep{stock2020b}.

@@

Finally, our causal model is framed using the language of structural equations models and causal diagrams of econometrics (\cite{pwright, haavelmo:1944, tinbergen:1940, wold:1954, pearl:biometrika}) and genetics \citep{wright1923},\footnote{The father and son, P. Wright (economist) and S. Wright (geneticist) collaborated to develop structural equation models and causal path diagrams; P. Wright's key work represented supply-demand system as a directed acyclical graph and established its identification using exclusion restrictions on instrumental variables. We view our work as following this classical tradition.} with natural unfolding potential/structural outcomes representation \citep{rubin1974,tinbergen1930,neyman:PO,imbens_rubin_2015}. The work on causal graphs has been modernized and put on rigorous footing by  \cite{pearl:biometrika} and others (\cite{pearl:robins}, \cite{pearl:causality}, \cite{pearl:why}, \cite{white:chalak},  \cite{heckman:pinto}, \cite{peters2020book}, and \cite{hernanrobins2020book}), with major applications taking place in computer science, epidemiology, and econometrics. The particular causal diagram we use has several ``mediation" components, where variables affect outcomes directly and indirectly through other variables called mediators; these structures go back at least to \citet[][see Figure 6]{wright1923}; see, e.g., \cite{baron1986}, \cite{Hines2020}, \cite{richardson:mediation} for modern treatments.

@@

The exogeneity restrictions on the stochastic shocks are as follows:
\begin{equation}\label{eqn:SEM2} \tag{E}
\begin{aligned}
   & \varepsilon^y_{it} &  \perp &  \quad (\varepsilon^b_{it}, \varepsilon^p_{it}, {\wcolor W_{it}}, {\icolor I_{it}}), \\
&  \varepsilon^b_{it}  & \perp & \quad  (\varepsilon^p_{it}, {\wcolor W_{it}}, {\icolor I_{it}}), \\
&   \varepsilon^p_{it} &  \perp &  \quad ({\wcolor W_{it}}, {\icolor I_{it}}),
\end{aligned}
\end{equation}
where we say that $V \perp U$ if $\Ep VU = 0$.\footnote{ An alternative useful
starting point is to impose the Rosenbaum-Rubin type unconfoundedness condition:
$$
Y_{i,t+\ell} (\cdot,\cdot,\cdot)  \indep (P_{it}, B_{it}, I_{it})  \mid W_{it}, \
B_{it} (\cdot,\cdot)  \indep (P_{it}, I_{it})  \mid W_{it}, \
 P_{it} (\cdot)  \indep  I_{it}  \mid W_{it},
$$
which imply, with treating stochastic errors as independent additive components, the orthogonal conditions stated above.
The same unconfoundedness restrictions can be formulated using formal causal DAGs, and also imply orthogonality restrictions stated above, once stochastic errors are modeled as independent additive components.} This is a standard way of representing restrictions on errors in structural equation modeling in econometrics.\footnote{The structural equations of this form are connected to triangular structural equation models, appearing in microeconometrics and macroeconometrics (SVARs), going back to the work of  \cite{strotz1960recursive}.}

@@

The specification of the model above grasps one-period responses.  The dynamics over multiple periods will be induced by the evolution
of information variables, which include time, lagged and integrated values of outcome:\footnote{Our empirical analysis also considers a specification in which information variables include lagged national cases/deaths as well as lagged behavior variables.}
\begin{equation}\label{eq:I}\tag{I}
 {\icolor I_{it} } := I(t, {\ycolor Y_{it}},  { \icolor  I_{i, t-1} })' := \Big (g(t) , {\ycolor Y_{it}},  \sum_{m=0}^{t/\ell}
{\ycolor Y_{i,t - \ell m}} \Big )  \end{equation}
 for  each  $t \in \{0,1,...,T\}$, where $g$ is deterministic function of time, e.g., month indicators,
 and $t/\ell$ is defined as $\lceil {t/\ell} \rceil$.

@@

\begin{quote}
\textsc{Structural Equations Model (SEM)}.  Let $i \in \{1,..., N\}$ denote the observational unit,  $t$ be the time periods, and $\ell$ be the time delay.  (1) For each $i$ and $t \leq -\ell$, the confounder, information, behavior, and policy variables $W_{it}, I_{it},  B_{it}, P_{it}$ are determined outside of the model, and the outcome variable $Y_{i, t+\ell}$ is determined by factors outside of the model for $t \leq 0$.  (2) For each $i$ and $t \geq -\ell$, confounders $W_{it}$ are  determined by factors outside of the mode, and information variables $I_{it}$ are determined  by (I); policy variables $P_{it}$ are determined by setting $\iota = I_{it}$  in (P) with  a realized stochastic shock $\varepsilon^p_{it}$ that obeys the exogeneity condition (E);  behavior variables $B_{it}$ are determined by setting $\iota = I_{it}$ and $p= P_{it}$ in  (SO) with a shock $\varepsilon^b_{it}$ that obeys (E); finally, the outcome $Y_{i, t + \ell}$ is realized by setting $\iota = I_{it}$, $p= P_{it}$, and $b = B_{it}$ in  (SO) with a shock $\varepsilon^y_{it}$ that obeys (E). \end{quote}

@@

We  also consider simple counterfactual exercises, where we examine the effects of setting
a sequence of counterfactual policies for each state:
\begin{equation} \label{p-cf}\tag{CF-P}
\{{\pcolor P^\star_{it}} \}_{t=1}^T, \quad i=1, \ldots N.
\end{equation}
We assume that the SEM remains invariant, except for the policy equation.\footnote{It is possible to consider counterfactual exercises in which policy  responds to information through the policy equation if we are interested in endogenous policy responses to information. Counterfactual experiments with endogenous government policy would be important, for example, to understand the issues related to the lagged response of government policies to higher infection rates due to incomplete information. } 
The assumption  of invariance captures the idea that counterfactual policy interventions would not change the structural functions within the period of the study.  The assumption is strong but is necessary to conduct
counterfactual experiments, e.g. \cite{sims1972money} and \cite{strotz1960recursive}. It captures the idea that counterfactual policy interventions would not change the structural functions within the period of the study. To make the assumption more plausible we limited our study to the early pandemic period.\footnote{Furthermore, we conducted several stability checks, for example, checking if the coefficients on mask policies remain stable (reported in the previous version) and also looking at more recent data during reopening, beyond early pandemic, to examine the stability of the model.}

Given the policies, we generate the counterfactual
outcomes, behavior, and information by propagating the dynamic equations:
\begin{equation} \label{eqn:CF-SEM} \tag{CF-SEM}
  \begin{aligned}
& {\ycolor Y^\star_{i,t+\ell}}  & := & Y_{i,t+\ell} ( {\bcolor B^\star_{it} } , {\pcolor P^\star_{it}}, {\icolor I^\star_{it}}), \\
& {\bcolor B^\star_{it} } & := &   B_{it}({\pcolor P^\star_{it} } ,{\icolor I^\star_{it}}), \\
& {\icolor I^\star_{it} }& := &  I ({ t,  {\ycolor Y^\star_{it}}, \icolor I^\star_{i,t-\ell}}),  \end{aligned}
\end{equation}
with the same initialization as the factual system up to $t \leq 0$. In stating this counterfactual system of equations, we assume that structural outcome equations (SO) and information equations (I) remain invariant and so do the stochastic shocks, decomposed
into observable and unobservable parts. Formally, we record this assumption and above discussion as follows.

\begin{quote}
\textsc{Counterfactual Structural Equations Model (CF-SEM)}.  Let $i \in \{1,..., N\}$ be the observational unit, $t$ be time periods, and $\ell$ be the time delay. (1) For each $i$ and $t \leq 0$, the confounder, information, behavior, policy, and outcome variables are determined as previously stated in SEM: $W^\star_{it}= W_{it}$, $I^\star_{it}= I_{it}$,  $B^\star_{it} = B_{it}$, $P^\star_{it}=P_{it}$, $Y^\star_{it} =Y_{it}$.  (2) For each $i$ and $t \geq 0$, confounders $W^\star_{it} =W_{it}$ are determined as in SEM, and information variables $I^\star_{it}$ are determined  by (I);  policy variables $P^\star_{it}$ are set in (\ref{p-cf}); behavior variables $B^\star_{it}$ are determined by setting $\iota = I^\star_{it}$ and $p= P^\star_{it}$ in  (SO) with  the same stochastic shock $\varepsilon^b_{it}$ in (SO); the  counterfactual outcome $Y^\star_{i, t + \ell}$ is realized by setting $\iota = I^\star_{it}$, $p= P^\star_{it}$, and $b = B^\star_{it}$ in  (SO) with the same stochastic shock $\varepsilon^y_{it}$ in  (SO).
\end{quote}

@@

The dynamic effects take the form:
$$
\begin{array}{lll}
  & \mathrm{DynE}^\star_{it} &=
  \sum_{m=1}^{t/\ell} \left( (\gamma \alpha)_2 + \mu_2+  (\gamma \alpha)_3+ \mu_3    \right)^m \left(\mathrm{PEB}^\star_{i,t-m \ell } +  \mathrm{PED}^\star_{i,t- m\ell} \right)
  \\
 &&  + \sum_{m=1}^{t/\ell-1} \left( (\gamma \alpha)_3 + \mu_3    \right)^m \left (\mathrm{PEB}^\star_{i,t-(m +1) \ell } +  \mathrm{PED}^\star_{i,t- (m+1)\ell}  \right),
 \end{array}
 $$
 interpreting $t/\ell$ as $\lceil t/\ell \rceil$, where $\mathrm{PEB}^\star_{i,t } =  \mathrm{PED}^\star_{i,t} = 0$
 for $t \leq 0$.  The effects can be decomposed into (a) delayed policy effects via behavior by
summing terms containing $PEB$ and (b) delayed policy effects via direct impact
by summing terms containing $PED$.

All counterfactual quantities and contrasts can be computed from the expressions given
above. For examples, given $\Delta C_{i0}>0$, new confirmed cases are linked to growth rates via relation:
$$
\frac{\Delta C^{\star}_{it}}{\Delta C_{i0}} = \exp\left (  \sum_{s=1}^t  Y^\star_{is} \right) \text{ and }\frac{ \Delta C_{it}}{\Delta C_{i0}} = \exp
\left (  \sum_{s=1}^t Y_{is}\right).
$$
The cumulative cases can be constructed by summing over the new cases. Various contrasts are
then calculated from these quantities. For example, the relative contrast of counterfactual new confirmed cases
to the  factual confirmed cases is given by:
$$
\Delta C^{\star}_{it}/\Delta C_{it} = \exp\left(  \sum_{s=1}^t ( Y^\star_{is} -  Y_{is}) \right).
$$
We refer to the appendix for further details. Similar calculations apply for fatalities. 
Note that our analysis is conditional on the factual history and structural stochastic 
shocks.\footnote{For unconditional counterfactual,
we need to make assumptions about the evolution of stochastic shocks appearing in $Y_{it}$. See, e.g, previous
versions of our paper in ArXiv, where unconditional counterfactuals were calculated by assuming stochastic shocks
are i.i.d. and resampling them from the empirical distribution. The differences between conditional and unconditional
contrasts were small in our empirical analysis.}
